On exponential sums arising from the classical doubling method

### 2025-04-11 main.tex
Typos

        \item (Types B,C,D Case 1) $w$ is conjugate to a cycle of length $n$. \calvin{Add in note about the two type B cases. Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\multiplcativeScheme}$ with $\Frobenius$ acting by $w$ on the domain and by the cycle $(w,w_n w w_n)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$

@@

		$$x_{\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}},\alpha \times \alpha^{-q}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$

>>>>

        \item (Types B,C,D Case 1) $w$ is conjugate to a cycle of length $n$. \calvin{Add in note about the two type B cases. Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\multiplcativeScheme}$ with $\Frobenius$ acting by $w$ on the domain and by the cycle $(w,w_n w w_n)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\multiplicativegroup{\finiteFieldExtension{n}},\alpha}).$$

@@

		$$x_{\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}},\alpha \times \alpha^{-q}} = \phi(x_{\multiplicativegroup{\finiteFieldExtension{n}},\alpha}).$$
